The \dealii Library, Version 9.2

### 2020-05-23 9.2/paper.tex
Add myself to author list.
Extension of hp-Interface.

\hypersetup{
  pdfauthor={
     Daniel Arndt,
     Wolfgang Bangerth,
%     Thomas C. Clevenger,
%     Denis Davydov,
%     Marc Fehling,
%     Daniel Garcia-Sanchez,
%     Graham Harper,
    Timo Heister,
%     Luca Heltai,
    Martin Kronbichler,
    Peter Munch,
%     Ross Maguire Kynch,
    Matthias Maier,
%     Jean-Paul Pelteret,
    Bruno Turcksin,
%     David Wells
  },
  pdftitle={The deal.II Library, Version 9.2, 2020},
}

@@

\todo[inline]{Marc: Your section}

>>>>

\hypersetup{
  pdfauthor={
     Daniel Arndt,
     Wolfgang Bangerth,
%     Thomas C. Clevenger,
%     Denis Davydov,
    Marc Fehling,
%     Daniel Garcia-Sanchez,
%     Graham Harper,
    Timo Heister,
%     Luca Heltai,
    Martin Kronbichler,
    Peter Munch,
%     Ross Maguire Kynch,
    Matthias Maier,
%     Jean-Paul Pelteret,
    Bruno Turcksin,
%     David Wells
  },
  pdftitle={The deal.II Library, Version 9.2, 2020},
}

@@

With the previous release, \dealii supports $hp$-adaptive finite element methods
on distributed memory systems \cite{dealII91}. We implemented the bare functionality
for $hp$-adaptive methods with the objective to offer the greatest flexibility in
their application. Here, reference finite elements still had to be assigned manually
to each cell, which may not lead to an optimal mesh and is tedious.

With the current release, $hp$-adaptive finite element methods have been further
expanded in both the range of features in terms of decision strategies and their 
user interface, effectively making the more attractive to use. We introduced many
new functions that automatize the general workflow for applying $hp$-decision
strategies, which run on top of the previous low-level implementation for both serial
and parallel applications.

The interface is now as simple to use as the one for pure adaptive mesh refinement.
Consider the following (incomplete) listing as an example: We estimate both error and
smoothness of the finite element approximation. Further, we flag certain fractions of
cells with the highest and lowest errors for refinement and coarsening, respectively
(here: 30\% / 3\%). From those cells listed for adaptation, we specify a subset of them
for $h$- and $p$-adaptation (here: 10\% / 90\%).
\begin{c++}
Vector<float> estimated_error_per_cell (n_active_cells);
KellyErrorEstimator::estimate(
  dof_handler, ..., solution, estimated_error_per_cell, ...);
GridRefinement::refine_and_coarsen_fixed_number(
  triangulation, estimated_error_per_cell, 0.3, 0.03);

Vector<float> estimated_smoothness_per_cell (n_active_cells);
SmoothnessEstimator::Legendre::coefficient_decay(
  ..., dof_handler, solution, estimated_smoothness_per_cell);
hp::Refinement::p_adaptivity_fixed_number(
  dof_handler, estimated_smoothness_per_cell, 0.9, 0.9);
hp::Refinement::choose_p_over_h (dof_handler);

triangulation.execute_coarsening_and_refinement();
\end{c++}

In particular, we implemented decision strategies based on refinement history and
smoothness estimation, and made sure that they work for refinement as well as
coarsening in terms of $h$- and $p$-adaptation in serial and parallel applications.

The former relies on knowing an estimate for the upper error bound \cite[Thm.~3.4]{BabuskaSuri1990}.
For successive refinements, we can predict how the error will change on basis of
current error estimates and adaptation flags. In the next refinement cycle, these
predicted error estimates allow us to decide whether the choice of adaptation in
the previous cycle was justified, and provide the foundation for it in the next
one \cite{MelenkWohlmuth2001}.

In general, $p$-refinement is favorable over $h$-refinement in smooth regions of
the finite element approximation \cite[Thm.~3.4]{BabuskaSuri1990}. Thus, estimating
its smoothness provides a suitable decision indicator for $hp$-adaptation. For this
purpose, we expand the finite element approximation into a series of orthogonal
basis functions of increasing complexity, and consider the decay of their expansion
coefficients as the estimation of smoothness. This has been implemented for both
Fourier coefficients \cite{BangerthKayserHerold2007} and Legendre coefficients
\cite{Mavriplis1994,HoustonSeniorSueli2003,HoustonSueli2005,EibnerMelenk2007}.
